Building new data for profiling
========================================================

This is a document to walkthough how to build a dataset for a new a profiling app. The app is built, that given the right data, will automatically update so no need for editing.

We are going to work with our first profiling: Techy vs. non-techy

```{r}
library(rCharts)
library(reshape2)
#install.packages("shiny")
library(shiny)

##Get micro cluster data
load(file="I:/201404/Mine4/02 Data/Sprint3/Clustering Solutions/micro_clusters.RData")
str(micro_clusters)
##Get original data for profiling.
load(file="I:/201404/Mine4/02 Data/Sprint3/sprint3_mine4_data_final.RData")
load(file='I:/201404/Mine4/02 Data/Sprint3/techi clusters/techy_pred.RData')

cluster.data.temp<-merge(sprint3.mine4.data,techy_pred,by="scv_id")
cluster.data.temp2<-merge(cluster.data.temp,micro_clusters[,c(1,7:10)],by="scv_id")
cluster.data.temp2$tenure_decile<-cut(cluster.data.temp2$tenure,
                                breaks=quantile(cluster.data.temp2$tenure, probs=seq(0,1, by=0.1)),
                                include.lowest=TRUE)
head(cluster.data.temp2[,c(1:10)])
```

You can see that our temporary data is at a scv_id level with the necessary inforamtion for modelling.

```{r fig.width=7, fig.height=6}
summary(cluster.data.temp2$classification)
```

It is very important that the profiling variable is called "classification", as this is what the code will search for when u put it into the app.

Lets pull out a subset of data to use for profiling:
```{r}
col.to.keep<-c(
  "age_band",
  "gender",
  "exp_h_property_type_v2_desc",
  "exp_h_outstand_mortgag_v2_desc",
  "exp_h_reg_n_hhld_inc_bnd_desc ",
  "exp_h_reg_n_property_bnd_desc",
  "exp_h_family_lifestg_2011_desc",
  "exp_h_mosaic_uk_group_desc",
  "exp_h_child_in_hhld_2011_desc",
  "exp_p_true_touch_group_desc",
  "tenure_decile",
  "classification",
  "platform_desc",
  "platform_desc_alt",
  "tod_desc",
  "content_desc"
)
cluster.data<-cluster.data.temp2[,colnames(cluster.data.temp2) %in% col.to.keep]
```

We also need to make sure the classification is a factor, and that it has meaningful factorl evels. This is also very important as this helps build out some of the commentary on the graphs and headline.

```{r}
cluster.data$classification<-as.factor(cluster.data$classification)
levels(cluster.data$classification)<-c("non-techy","techy")
```

Easy Peasy! You now have a dataset at a single user level, with a factor variable called "classification". THats all the app needs now to run so savethis into the data directory of your app. the current directory is below:

```{r}
write.csv(cluster.data,file="I:\\201404\\Mine4\\02 Data\\Sprint3\\Cluster profiling\\profile-app\\data\\cluster_data.csv",row.names=FALSE)
```

You're done! Now just run the app using shiny's runApp:

```{r eval=FALSE}
runApp("I:\\201404\\Mine4\\02 Data\\Sprint3\\Cluster profiling\\profile-app")
```
